Exposing Disputed Statements on the Web

### 2009-03-19 papers/uist_thinklink/thinklink.tex
Related work changes

@@

@@

>>>>

Think Link builds on work in several different areas. The argumentation structure influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987}; the idea of highlighting information that may not be trustworthy was previously applied to Wikipedia by Wiki-Trust~\cite{Adler2008}; the model of using a community to collect and filter information from a range of sources is influenced by tagging systems~\cite{Marlow2006}; and the idea of gathering up a collection of snippets from web pages has been used by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.

What makes Think Link interesting is the way that it combines ideas from these different domains and applies them to the task of leading users towards information that conflicts with that which they read.

@@

Hypertext systems such as Notecards~\cite{Halasz1988}.

@@

\subsection{Semantic Web}

Nobody is going to mark up their own web page as being wrong.
